Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect

### 2021-06-13 paper_draft3.tex
Rework

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}

@@

@@

We consider the following integro-difference equation
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
where 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } u < a, \\
1, & \text{if } a \leq u \leq b, \\
m, & \text{if } u > b,
\end{cases}
\end{equation}
with $0<a<m<b<1$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,m)$ with $a$ the Allee threshold value.

@@

In this section, we generalize the theory of traveling wave solutions of \ref{q} to the theory of periodic traveling waves.

Let $C(\mathbb R)$ denote the space of continuous functions $\mathbb R\to\mathbb R$ equipped with the supremum-norm $||u||_\infty=\sup_{x\in\mathbb R}|u(x)|$ for any $u\in C(\mathbb R)$.

For the remainder of the paper, we assume the following hypothesis on the dispersal kernel:

@@

\begin{hyp} \label{hypothesis1} The disperal kernel $k$ is Lebesgue measurable, and

\begin{enumerate}[i.)]
\item $k$ is non-negative, and $\int_{-\infty}^{\infty} k(x) \, dx = 1$;

@@

\item  for all $y\in\mathbb R$, for all $\mu\in(0,1)$, the function $f(x)= k(x)-\mu k(x-y)$ has at most one zero-crossing on $\mathbb R$.
\end{enumerate}
\end{hyp}

@@

Assuimption i. implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=m$. Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic. Assumption iii. guarantees a unique right-inverse satisfying $w_1(w_1^{-1}(p))=p$ for $0<p<1$.

\begin{lem} \label{lemma1}
If condition (x) is satisfied then $Q[w_2](x)=w_1(x-2c^*)$ for a unique $c^*\in\mathbb R$.
\end{lem}

\begin{proof} Let $\alpha,\beta\in\mathbb R$ such that $w_1(\alpha)=a$ and $w_1(\beta)=b$.  By the definition of $w_1$, it is decreasing and satisfies $w_1(-\infty)=1$ and $w_1(\infty)=0$, hence $\alpha$ and $\beta$ are unique.  Applying the growth function $g$ yields
\begin{equation} \label{gw1}
g(w_1(x)) = \begin{cases}
m & x < \beta \\
1 & \beta \leq x \leq \alpha \\
0 & x > \alpha
\end{cases} \end{equation}
Applying the convolution operator yields a formula for $w_2(x)$:
\begin{equation} \label{w2}
\begin{aligned}
w_2(x) &= \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy \\
&= \int_{x-\alpha}^{x-\beta} k(y)\,dy + \int_{x-\beta}^{\infty} m k(y)\,dy \\
&= \int_{x-\alpha}^{\infty} k(y)\,dy - \int_{x-\beta}^{\infty} (1-m) k(y)\,dy
\end{aligned}
\end{equation}
Taking the derivative with respect to $x$, we find
\begin{equation}
\frac{dw_2}{dx} = -k(x-\alpha) + (1-m)k(x-\beta)
\end{equation}
It follows from assumption iv. of \ref{hypothesis1} that $dw_2/dx$ has at most one zero-crossing. Hence, $w_2$ has at most one turning point. This leaves two cases: either $w_2$ has no turning points and is monotonically decreasing, or it has one turning point, to the left of which $w_2$ is increasing and to the right it is decreasing. In both cases, $w_2$ has a continuous right inverse on the open interval $(0,m)$.

Since $0<a<m$, we can take $x_0=w_2^{-1}(a)$  so that $w_2$ exceeds the Allee threshold to the left of $x_0$ and is below the Allee threshold on the right. Applying the growth function,
\begin{equation} \label{gw2}
g(w_2(x)) = \begin{cases}
1 & x \leq w_2^{-1}(a) \\
0 & x > w_2^{-1}(a)
\end{cases} \quad \text{almost everywhere}
\end{equation}
Applying the integro-difference operator, we obtain
\begin{equation}
Q[w_2](x) = \int_{x-w_2^{-1}(a)}^{\infty} k(y)\,dy = w_1(x-w_2^{-1}(a)).
\end{equation}
By defining $c^* = \frac{1}{2}w_2^{-1}(a)$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
\begin{equation}
Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
\end{equation}
\end{proof}

\begin{thm} \label{theorem1}
If $||w_2||_\infty\leq b$, then the sequence $(u_n)_{n=0}^{\infty}$ defined by
\begin{equation} \label{ptw}
u_{2n}(x) = w_1(x-2nc^*), \quad 
u_{2n+1}(x) = w_2(x-2nc^*)
\end{equation}
satisfies $u_{n+1}=Q[u_n]$ for all $n\geq 0$.
\end{thm}

\begin{proof}
By induction on $n$. For $n=0$, we have $u_0(x)=w_1(x)$ and $u_1(x)=Q[w_1](x)=w_2(x)$ by definition.

For the inductive step, assume $u_{2n}(x) = w_1(x-2nc^*)$ and $u_{2n+1}(x) = w_2(x-2nc^*)$ for some $n\geq 0$. By Lemma \ref{lemma1} and the translation invariance property of $Q$, we have
\begin{equation} \begin{aligned}
u_{2n+2}(x) = w_1(x-2nc^*-2c^*) = Q[w_2](x-2nc^*) = Q[u_{2n+1}](x)
\end{aligned} \end{equation}
 Likewise,
\begin{equation}
u_{2n+3}(x) = w_2(x-2nc^*-2c^*) = Q[w_1](x-2nc^*-2c^*) = Q[u_{2n+2}](x).
\end{equation}
\end{proof}

@@

In this section, we construct the population density functions $w_1$ and $w_2$ for several choices of dispersal kernel.

@@

One can easily verify conditions i. - iii. of Hypothesis 2.1. To check condition iv., we introduce the following lemma:

\begin{lem}
The Laplace kernel \eqref{laplacekernel} satisfies condition (iv.) of Hypothesis 2.1.
\end{lem}

We have shown that the Laplace kernel satisfies Hypothesis 2.1; thus, we can construct a periodic traveling wave solution:

\begin{equation}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
\begin{equation}\label{laplacew2}
w_2(x) = \int_{x-\winva}^{\infty} \frac{1}{2} e^{-|y|} \,dy - \int_{x-\winvb}^{\infty} \frac{1-m}{2} e^{-|y|} \,dy
\end{equation}
with
$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$

The integrals in \eqref{laplacew2} can be computed using elementary methods to obtain
\begin{equation}
w_2(x) = \begin{cases}
\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
\end{cases}
\end{equation}

We can split into three cases:

\begin{enumerate}
\item $a<\frac{1}{2}$, $b<\frac{1}{2}$. Then
\begin{equation}
w_2(x) = \begin{cases}
\frac{1}{2} e^x \left( e^{-w_1^{-1}(b)} -e^{-w_1^{-1}(a)} \right)  & x < w_1^{-1}(b) \\
1 - \frac{1}{2} e^{x-w_1^{-1}(a)} - \frac{1}{2} e^{-(x-w_1^{-1}(b))} & w_1^{-1}(b) < x < w_1^{-1}(a) \\
\frac{1}{2} e^{-x} \left(  e^{w_1^{-1}(a)} - e^{w_1^{-1}(b)} \right) & x > w_1^{-1}(a)
\end{cases}
\end{enumerate}

Then
$$ w_2(x) = \begin{cases}
\int_{-\infty}^{-\log(2b)} \frac{m}{2}e^{-|x-y|}\,dy + \int_{-\log(2b)}^{-\log(2a)} \frac{1}{2}e^{-|x-y|} \,dy & a<\frac{1}{2}, b < \frac{1}{2} \\
\int_{-\infty}^{\log(2-2b)} \frac{m}{2}e^{-|x-y|} \,dy + \int_{\log(2-2b)}^{-\log(2a)} \frac{1}{2}e^{-|x-y|} \,dy & a<\frac{1}{2}, b \geq \frac{1}{2} \\ 
\int_{-\infty}^{\log(2-2b)} \frac{m}{2}e^{-|x-y|} \,dy + \int_{\log(2-2b)}^{\log(2-2a)} \frac{1}{2}e^{-|x-y|} \,dy & a\geq\frac{1}{2}, b \geq \frac{1}{2} \\
\end{cases} $$
Now make the substitution $y'=x-y$.
$$ w_2(x) = \begin{cases}
\int_{x+\log(2b)}^{\infty} \frac{m}{2}e^{-|y'|}\,dy' + \int_{x+\log(2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y'|} \,dy' & a<\frac{1}{2}, b < \frac{1}{2} \\
\int_{x-\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y'|} \,dy' + \int_{x-\log(2-2b)}^{x+\log(2a)} \frac{1}{2}e^{-|y'|} \,dy' & a<\frac{1}{2}, b \geq \frac{1}{2} \\ 
\int_{x-\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y'|} \,dy' + \int_{x-\log(2-2b)}^{x-\log(2-2a)} \frac{1}{2}e^{-|y'|} \,dy' & a\geq\frac{1}{2}, b \geq \frac{1}{2} \\
\end{cases} $$

Conversely, we may define $\sigma_p=\text{sign}(p-\frac{1}{2})$. Then, we have $w_1^{-1}(p)=\sigma_p\log(\sigma_p(2p+1)+1)$. The above equation then simplifies to
\begin{equation}
w_2(x) = \int_{-\infty}^{\sigma_a\log(\sigma_a(2a+1)+1)} mk(x-y)\,dy + \int_{\sigma_b\log(\sigma_b(2p+1)+1)}^{\sigma_a\log(\sigma_a(2a+1)+1)} k(x-y)\,dy
\end{equation}

We will now split into further cases.

Case 1: $a<b<\frac{1}{2}$. Then
$$ w_2(x) = \int_{x-\log(2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x-\log(2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$
We can expand this out using $\min$ and $\max$ functions. Let $x_a=x-\log(2a)$ and $x_b=x-\log(2b)$. Then
$$ w_2(x) = \int_{\min(x_b,0)}^0 \frac{m}{2} e^y \, dy + \int_{\max(x_b,0)}^{\infty} \frac{m}{2} e^{-y} \, dy
+ \int_{\min(x_b,0)}^{\min(x_a,0)} \frac{1}{2} e^y \, dy + \int_{\max(x_b,0)}^{\max(x_a,0)} \frac{1}{2} e^{-y} \, dy $$
We can now take the integral:
$$ \frac{m}{2} - \frac{m}{2} e^{\min(x_b,0)} - \frac{m}{2} e^{-\max(x_b,0)} + \frac{1}{2} e^{\min(x_a,0)} - \frac{1}{2} e^{\min(x_b,0)} - \frac{1}{2} e^{-\max(x_a,0)} + \frac{1}{2} e^{-\max(x_b,0)} $$
This is equal to
$$ \frac{m}{2} - \frac{m}{2} \min(e^{x_b},1) - \frac{m}{2} \min(e^{-x_b},1) + \frac{1}{2} \min(e^{x_a},1) - \frac{1}{2} \min(e^{x_b},1) - \frac{1}{2} \min(e^{-x_a},1) + \frac{1}{2} \min(e^{-x_b},1) $$
$$ = \frac{m}{2} - \frac{m+1}{2} \min(e^{x_b},1) - \frac{m+1}{2} \min(e^{-x_b},1) - \frac{1}{2} \min(e^{x_a},1) - \frac{1}{2} \min(e^{-x_a},1)$$
$$ = \frac{m}{2} - \frac{m+1}{2}\left( \min(e^{x_b},1) - \min(e^{-x_b},1) \right) - \frac{1}{2} \left( \min(e^{x_a},1) - \min(e^{-x_a},1) \right) $$

$$ = \frac{m}{2} - \frac{m+1}{2}\left( \min(2be^{-x},1) - \min(\frac{1}{2b}e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$

It can be written in three cases

$$ w_2(x) = \begin{cases} \displaystyle
m - \frac{am+a-b}{4ab} e^x & x <\log(2a) \\
\displaystyle
m + 1 - \frac{m+1}{4b} e^x - ae^{-x} & \log(2a) \leq x \leq \log(2b) \\
\displaystyle
(mb+b-a) e^{-x}  & x > \log(2b)
\end{cases} $$

Since $w_2$ is increasing for $x<\log(2a)$, we know the solution to $w_2(x)=a$ must lie on the second or third pieces. This can be determined by checking the sign of $w_2(\log(2b))-a$. If it is positive, the horizontal line $y=a$ intersects the curve $y=w_2(x)$ on the third piece, and the solution can be found by solving $(mb+b-a)e^{-x}=a$. Otherwise, if the sign is negative, the solution occurs on the second piece as the solution to the equation

$$ w_2(x)=a \iff m + 1 - \frac{m+1}{4b} e^x - ae^{-x} = a $$

First let us group like terms and multiply by $4b$:

$$ (m+1) e^x + (m + 1 - a) - 4abe^{-x} = 0 $$

Using the substitution $y=e^x$, this equation becomes a quadratic in $y$:

$$ (m+1) y^2 + (m + 1 - a) y - 4ab = 0 $$

The solution is

$$ y = \frac{a-m-1 \pm \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2}$$

We know the global maximum of $w_2(x)$ lies somewhere in the open interval $(\log(2a),\log(2b))$, therefore we take the greater solution so that

$$ c^* = \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) $$

Then we can obtain the critical wave speed in two cases:
$$ c^* = \begin{cases} \displaystyle
\frac{1}{2} \log \left( \frac{mb+b-a}{a} \right) & m \geq \frac{2ab+a-b}{b} \\
\displaystyle
 \frac{1}{2} \log\left(  \frac{a-m-1 + \sqrt{(m+1-a)^2 + 16ab(m+1)}}{2m+2} \right) & m < \frac{2ab+a-b}{b}
\end{cases} $$

Case 2: $a<\frac{1}{2}<b$. Then
$$ w_2(x) = \int_{x+\log(2-2b)}^{\infty} \frac{m}{2}e^{-|y|}\,dy + \int_{x+\log(2-2b)}^{x-\log(2a)} \frac{1}{2}e^{-|y|} \,dy $$

Then

$$ w_2(x) = \frac{m}{2} - \frac{m+1}{2}\left( \min(\frac{e^{-x}}{2-2b},1) - \min((2-2b)e^{x},1) \right) - \frac{1}{2} \left( \min(2ae^{-x},1) - \min(\frac{1}{2a}e^{x},1) \right) $$

so

$$ w_2(x) = \begin{cases}
\displaystyle
m - \frac{4a(m+1)(1-b)-1}{4a} e^x & x <\log(2a) \\
\displaystyle
m+1 - (m+1)(a-b) e^x - ae^{-x} & \log(2a) \leq x \leq -\log(2-2b) \\
\displaystyle
\frac{m+1-4a(1-b)}{4(1-b)} e^{-x}  & x > -\log(2-2b)
\end{cases} $$

>>>>

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}
\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\newcommand{\m}{\mu}

@@

{\bf Todo:} Proof of Theorem 2.2.
\newline

@@

We consider the following integro-difference equation
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
where 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } u < \a, \\
1, & \text{if } \a \leq u \leq \b, \\
\m, & \text{if } u > \b,
\end{cases}
\end{equation}
with $0<\a<\m<\b<1$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,\m)$ with $\a$ the Allee threshold value.

@@

In this section, we construct a periodic traveling wave solution to the recurrence \eqref{q}. We will assume the dispersal kernel $k$ satisfies the following hypotheses:

@@

%\begin{hyp} \label{hypothesis1} The disperal kernel $k$ is Lebesgue measurable, and

\begin{enumerate}[(H1)]
\item $k$ is a non-negative Lebesgue-integrable function with $\int_{-\infty}^{\infty} k(x) \, dx = 1$;

@@

\item  for all $\lambda\in(0,1)$, for all $y\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-y)$ has at most one zero-crossing in $\mathbb R$.
\end{enumerate}
%\end{hyp}

Under these assumptions, the cumulative density function $F(x)=\int_{-\infty}^{x}k(y)\,dy$ has a well-defined right inverse $F^{-1}$ satisfying $F(F^{-1}(p))=p$ for all $0<p<1$. Furthermore, it satisfies the symmetry relation $F(-x)=1-F(x)$.

@@

Hypothesis (H1) implies $w_1$ and $w_2$ have well-defined limits at $\pm\infty$ given by $w_1(\infty)=w_2(\infty)=0$, $w_1(-\infty)=1$, and $w_2(-\infty)=\m$. Furthermore, $w_1$ is monotonically decreasing, while $w_2$ may be non-monotonic.

\begin{lem} \label{lemma1}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then there exists unique $c^*\in\mathbb R$ such that $Q[w_2](x)=w_1(x-2c^*)$ for all $x\in\mathbb R$.
\end{lem}

\begin{proof} Let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$. It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Thus, composing $w_1(x)$ with the growth function $g$ yields
\begin{equation} \label{gw1}
g(w_1(x)) = \begin{cases}
\mu & x < x_\beta \\
1 & x_\beta \leq x \leq x_\a \\
0 & x > x_\a
\end{cases} \end{equation}

Applying the convolution operator yields a formula for $w_2(x)$:
\begin{equation} \label{w2calculation}
\begin{aligned}
w_2(x) &= \int_{-\infty}^{\infty} k(y) g(w_1(x-y)) \, dy \\
&= \int_{x-x_\a}^{x-x_\b} k(y)\,dy + \m \int_{x-\beta}^{\infty} k(y)\,dy \\
&= \int_{x-x_\a}^{\infty} k(y)\,dy - (1-\m) \int_{x-x_\b}^{\infty} k(y)\,dy
\end{aligned}
\end{equation}

Taking the derivative with respect to $x$, we find
\begin{equation}\label{dw2dx}
\frac{dw_2}{dx} = -k(x-x_\a) + (1-\m)k(x-x_\b)
\end{equation}

From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point. This leaves two cases:
\begin{enumerate}[{Case} 1.]
\item If $w_2$ has no turning points, it must be monotonically decreasing.
\item If $w_2$ has a single turning point $x^*$, then $w_2(x)$ is increasing on $(-\infty,x^*)$ and decreasing on $(x^*,\infty)$, with $\m \leq w_2(x^*)\leq \b$.
\end{enumerate}

In both cases, $w_2(x)$ has a well-defined right inverse on the open interval $(0,\m)$. Since $0<\a<\m$, let
\begin{equation}
c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid w_2(x)\geq\a\}
\end{equation}

It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can compose with $g$ as follows:
\begin{equation} \label{gw2}
g(w_2(x)) = \begin{cases}
1 & x \leq 2c^* \\
0 & x > 2c^*
\end{cases} \end{equation}

Taking convolution with $k$, we obtain
\begin{equation}
Q[w_2](x) = \int_{x-x_0}^{\infty} k(y)\,dy = w_1(x-2c^*).
\end{equation}
%By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
%\begin{equation}
%Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
%\end{equation}
\end{proof}

\begin{thm} \label{theorem1}
If $\sup_{x\in\mathbb R}w_2(x)\leq \b$, then the recurrence \eqref{q} has a periodic traveling wave solution given by
\begin{equation} \label{ptw}
W_n(x) = \begin{cases}
w_1(x-nc^*) & n \text{ even} \\
w_2(x-nc^*) & n \text{ odd}
\end{cases}
\end{equation}
\end{thm}

\begin{proof}
DO THIS
\end{proof}

@@

In this section, we construct the periodic traveling wave solution for several well-known disperal kernels in population biology, namely the uniform, Laplace, and normal distributions. For the uniform and Laplace kernels, we were able to construct a piecewise expression for the mean wave speed in terms of the model parameters.

@@

The reader can easily verify that the Laplace kernel satisfies hypotheses (H1) - (H3). The proof that is also satisfies (H4) is left in the appendix. The periodic traveling waves are given by

\begin{equation}
w_1(x) =   \begin{cases} 
1 - \frac{1}{2}e^{x} & x \leq 0 \\
\frac{1}{2}e^{-x} & x > 0
\end{cases}
\end{equation}
and
%\begin{equation}\label{laplacew2}
%w_2(x) = \begin{cases}
%m - \frac{1}{2} e^{x - \alpha} + \frac{1-\m}{2} e^{x - \beta} & x < \beta \\
%1 - \frac{1}{2} e^{x-\alpha} - \frac{1-\m}{2} e^{-(x-\beta)} & \beta \leq x \leq \alpha \\
%\frac{1}{2} e^{-(x-\alpha)} - \frac{1-\m}{2} e^{-(x-\beta)} & x > \alpha
%\end{cases}
%\end{equation}
\begin{equation}
w_2(x) = \begin{cases}
m + C_1 e^x & x < \beta \\
1 - C_2 e^x - C_3 e^{-x} & \beta < x < \alpha \\
C_4 e^{-x} & \alpha < x 
\end{cases} \end{equation}
where $\alpha=w_1^{-1}(\a)$, $\beta=w_1^{-1}(\b)$, with
$$ w_1^{-1}(p) = \begin{cases} -\ln(2p) & p\leq \frac{1}{2} \\ \ln(2-2p) & p > \frac{1}{2} \end{cases} $$
The constants $C_1,C_2,C_3$, and $C_4$ are continuous functions of the growth parameters, with $C_2,C_3,C_4\geq0$, and they are given by
\newcommand{\Conecaseone}{\b(1-\m)-\a}
\newcommand{\Conecasetwo}{\frac{1-\m-4\a(1-\b)}{4(1-\b)}}
\newcommand{\Conecasethree}{- \frac{1-\b+\m(1-\a)}{4(1-\a)(1-\b)} }

\begin{equation}
C_1 = \begin{cases}
\Conecaseone & \a,\b < \frac{1}{2} \\
\Conecasetwo & \a<\frac{1}{2}<\b \\
\Conecasethree & \frac{1}{2}<a,b
\end{cases} \end{equation}

\newcommand{\Ctwocaseone}{\a}
\newcommand{\Ctwocasetwo}{\frac{1}{4(1-\a)}}

\begin{equation}
C_2 = \begin{cases}
\Ctwocaseone & \a < \frac{1}{2} \\
\Ctwocasetwo & \a > \frac{1}{2}
\end{cases} \end{equation}

\newcommand{\Cthreecaseone}{\frac{1-\m}{4\b}}
\newcommand{\Cthreecasetwo}{(1-\m)(1-\b)}

\begin{equation}
C_3 = \begin{cases}
\Cthreecaseone & \b < \frac{1}{2} \\
\Cthreecasetwo & \b > \frac{1}{2}
\end{cases} \end{equation}

\newcommand{\Cfourcaseone}{\frac{\b-\a(1-m)}{4\a\b}}
\newcommand{\Cfourcasetwo}{\frac{1-4\a(1-\m)(1-\b)}{4\a}}
\newcommand{\Cfourcasethree}{1-\a-(1-\m)(1-\b)}

\begin{equation}
C_4 = \begin{cases}
\Cfourcaseone & \a,\b < \frac{1}{2} \\
\Cfourcasetwo & \a<\frac{1}{2}<\b \\
\Cfourcasethree & \frac{1}{2}<a,b
\end{cases} \end{equation}

To find $c^*$, we can now condition on the values of $w_2(\alpha)$ and $w_2(\beta)$.
% If $w_2(\alpha)=C_4e^{-\alpha}>a$, then we know $x_a>\alpha$, so that $C_4e^{-x_a}=C_4e^{-2c^*}=a$ implies $c^*=\frac{1}{2}\ln(\frac{C_4}{a})$.
%
%If $w_2(\alpha)<a$ and $w_2(\beta)>a$, then we solve the equation
%
%$$ 1 - C_2e^x - C_3e^{-x} = a $$
%
%Multiplying through by $e^x$ yields a quadratic in $e^x$:
%
%$$ e^x - C_2e^{2x} - C_3 = ae^x $$
%
%$$ C_2 e^{2x} + (a-1) e^x + C_3 = 0 $$
%
%$$ e^x = \frac{1-a \pm \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} $$
%
%Since $C_2,C_3$ are negative, we know the function is concave down on this piece. Therefore, we take the rightmost solution, since the curve must be increasing through this point since the solution is unique.
%
%$$ c^* = \frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) $$
%
%In the final case where $w_2(\beta)<a$, we have
%
%$$ m + C_1 e^{x_a} = a $$
%implies
%$$ C_1e^{x_a} = a-m$$
%$$ x_a = \ln \frac{a-m}{C_1} $$
%$$ c^* = \frac{1}{2} \ln \frac{a-m}{C_1} $$
%
%Our general formula is thus
%\begin{equation}
%c^* = \begin{cases}
%\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<w_2(\alpha) \\
%\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & w_2(\alpha)<a<w_2(\beta) \\
%\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>w_2(\beta)
%\end{cases}
%\end{equation}
%Equivalently,
\begin{equation}
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{C_4}{a} \right) & a<C_4e^{-\alpha} \\
\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4C_2C_3}}{2C_2} \right) & C_4e^{-\alpha}<a<m+C_1e^\alpha\\
\frac{1}{2} \ln \left( \frac{a-m}{C_1}\right) & a>m+C_1e^\alpha
\end{cases}
\end{equation}

Since the form of $w_2(x)$, and thus of $c^*$, depends on the values of $\a$ and $\b$; thus we will split into three cases for further analysis.

%Let $c_1$ and $c_2$ denote the intermediate wave speeds measured at some threshold $0<h<m$. For this analysis we chose the threshold of $h=a$. Thus $c_1 = w_2^{-1}(a) - w_1^{-1}(a)=2c^*-\alpha$, and $c_2=2c^*+\alpha-c_1=2\alpha$. We can now define the relative fluctuation in wavespeed by
%
%$$ f = \frac{|c_1-c_2|}{c^*} = \frac{|2c^*-3\alpha|}{c^*} $$
%
%We can also consider
%
%$$ f^2 = \frac{(c_1-c_2)^2}{(c^*)^{2}} $$
%
%The derivative is
%
%$$ \frac{df^2}{da} = \frac{d}{da}(c_1-c_2)^2\frac{1}{(c^*)^2} $$
%
%$$ = 2(c_1-c_2)(\frac{dc_1}{da}-\frac{dc_2}{da})(c^*)^{-2} - 2(c_1-c_2)^2(c^*)^{-3} $$
%
%$$ = \frac{2(c_1-c_2)}{(c^*)^2}\left((\frac{dc_1}{da}-\frac{dc_2}{da}) - \frac{c_1-c_2}{c^*}\right) $$
%
%It follows that $f$ is differentiable with respect to all the parameters almost everywhere. We conjecture that
%
%$$ \frac{df}{da} \geq 0 , \quad \text{almost everywhere} $$
%
%We will first consider the case $a,b<\frac{1}{2}$, and $a<C_4e^{-\alpha}$. We then have $\alpha=-\ln(2a)$, $c^*=\frac{1}{2}\ln\frac{b-(1-m)a}{4a^2b}$ so that
%
%$$ f = \frac{|\ln\frac{b-(1-m)a}{4a^2b}+3\ln(2a)|}{\ln\frac{b-(1-m)a}{4a^2b}} $$
%$$ = \frac{|\ln(2a(b-(1-m)a))-\ln(b)|}{\ln(b-(1-m)a)-\ln(4a^2b)}  $$

\begin{enumerate}[{Case} 1.]

\item $\a<\frac{1}{2}$, $\b<\frac{1}{2}$.
\begin{equation}
w_2(x) = \begin{cases}
\m + (\Conecaseone) e^x  & x < -\ln(2\b) \\
1 - \Ctwocaseone e^x - \Cthreecaseone e^{-x} & -\ln(2\b) < x < -\ln(2\a) \\
\Cfourcaseone e^{-x} & x > -\ln(2\a)
\end{cases}
\end{equation}

We have $w_2(\alpha)=\frac{\b-\a(1-\m)}{2\b}$ and $w_2(\beta)=\m + \frac{\b(1-\m)-\a}{2\b}$. Thus,
\begin{equation}
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{\b-\a(1-\m)}{4\a^2\b} \right) & \a < \frac{\b-\a(1-\m)}{2\b} \\
\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - \frac{\a(1-m)}{b}}}{2\a} \right) & \frac{\b-\a(1-\m)}{2\b} < a < \frac{\b(1+\m)-\a}{2\b} \\
\frac{1}{2} \ln \left( \frac{a-m}{\b(1-\m)-\a}\right) & a > \frac{\b(1+\m)-\a}{2\b}
\end{cases}
\end{equation}

\item $\a<\frac{1}{2}$, $\b>\frac{1}{2}$.
\begin{equation}
w_2(x) = \begin{cases}
\m + \Conecasetwo e^x  & x < \ln(2-2\b) \\
1 - \Ctwocaseone e^x - \Cthreecasetwo e^{-x} & \ln(2-2\b) < x < -\ln(2\a) \\
\Cfourcasetwo e^{-x} & x > -\ln(2\a)
\end{cases}
\end{equation}

We have $w_2(\alpha)=\frac{1-4\a(1-\m)(1-\b)}{2}$ and $w_2(\beta)=\frac{1+\m-4\a(1-\b)}{2}$. Thus,
\begin{equation}
c^* = \begin{cases}
\frac{1}{2} \ln \left( \frac{1-4\a(1-\m)(1-\b)}{4\a^2} \right) & a<\frac{1-4\a(1-\m)(1-\b)}{2} \\
\frac{1}{2} \ln \left( \frac{1-a + \sqrt{(1-a)^2 - 4a(1-\m)(1-\b)}}{2a} \right) & \frac{1-4\a(1-\m)(1-\b)}{2}<a<\frac{1+\m-4\a(1-\b)}{2} \\
\frac{1}{2} \ln \left( \frac{4(a-m)(1-b)}{1-\m-4\a(1-\b)}\right) & a>\frac{1+\m-4\a(1-\b)}{2}
\end{cases}
\end{equation}

\item $\a>\frac{1}{2}$, $\b>\frac{1}{2}$.
\begin{equation}
w_2(x) = \begin{cases}
\m \Conecasethree e^x  & x < \ln(2-2\b) \\
1 - \Ctwocasetwo e^x - \Cthreecasetwo e^{-x} & \ln(2-2\b) < x < \ln(2-2\a) \\
(\Cfourcasethree) e^{-x} & x > \ln(2-2\a)
\end{cases}
\end{equation}

Thus, $w_2(\alpha)=\frac{1-\a-(1-\m)(1-\b)}{2(1-a)}$ and $w_2(\beta)=\m - \frac{1-\b+\m(1-\a)}{2(1-\a)}$
